Introduction to Natural Language Processing

### 2007-07-12 slides/baypiggies.tex
- Added some content for part 3 (case studies)
svn/trunk@4875

\documentclass{beamer}             % for slides
% \documentclass[handout]{beamer}    % for handout
\input{beamer}

@@

\subsection{??}

@@

>>>>

\documentclass{beamer}             % for slides
\usepackage{alltt}
% \documentclass[handout]{beamer}    % for handout
\input{beamer}

@@

@@

\subsection{Text Classificaiton}

\begin{frame}
  \frametitle{Text Classification}
  \begin{itemize}
    \item Choose the most appropriate label for each piece of text.
    \begin{itemize}
      \item Topic classification
      \item Spam Filtering
      \item Word Sense Disambiguation
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Features}
  \begin{itemize}
    \item To decide which label is appropriate for a text, 
      classifiers look at \emph{features} of that text.
    \item Features indicate what aspects of the text are
      relevant for the classification task.
    \item Features are typically hand-crafted for a given task.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Classifying in NLTK}
  \begin{itemize}
    \item Classifiers are applied to \emph{featuresets}:
\begin{alltt}\small
>>> animal = dict(fur=True, legs=4, 
                  size='large', spots=True)
>>> my_classifier.classify(animal)
'leopard'
\end{alltt}
    \item Features are found with a \emph{feature extractor}:
\begin{alltt}\small
>>> def document_features(document):
...     return dict([('contains-word(%s)'%w,True) 
...                  for w in document])
\end{alltt}
    \item Training:
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Demo -- Predict Genders of Names}
  \begin{itemize}
  \item Given a new name, that we've never seen before, predict
    whether it is male of female.
  \item Use the \texttt{names} corpus.
  \end{itemize}
\end{frame}

\subsection{Distributional Similarity}

\begin{frame}
  \frametitle{Word Similarity?}
  \begin{itemize}
  \item It's useful to know whether two words are similar
    \begin{itemize}
    \item ...
    \end{itemize}
  \item Different notions of \emph{similarity}:
    \item What words tend to co-occur?
    \item What words occur in similar contexts?
  \end{itemize}
\end{frame}
